---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pacose

`pacose` estimates partial correlation and precision matrices when a graph
specifies conditional independence constraints. It provides Ridge, PLS, LASSO,
adaptive LASSO, iPACOSE, MVUE, SURE and INVEST estimators.

## Installation

Install the development version from GitHub:

```r
remotes::install_github("vguillemot/pacose")
```

## Example

The graph below encodes the allowed non-zero entries of a precision matrix.
The Ridge version estimates the constrained precision matrix from simulated
observations.

```{r example}
library(igraph)
library(pacose)

set.seed(1)
omega <- matrix(c(1, .4, 0, 0,
                  .4, 1, .3, 0,
                  0, .3, 1, .2,
                  0, 0, .2, 1), nrow = 4, byrow = TRUE)
graph <- graph_from_adjacency_matrix(omega != 0, mode = "undirected",
                                     diag = FALSE)
X <- mvtnorm::rmvnorm(100, sigma = solve(omega))

fit <- pacose.ridge(X, graph, cv.method = "HKB")
round(fit$invcov, 2)
```

## Reference

Guillemot V., Bender A., Boulesteix A.-L. (2013). *Iterative Reconstruction of
High-Dimensional Gaussian Graphical Models Based on a New Method to Estimate
Partial Correlations under Constraints*. **PLOS ONE**, 8(4), e60536.
<https://doi.org/10.1371/journal.pone.0060536>
